Analysis and results

### 2020-09-11 analysis/03_analysis.Rmd
Updated covariate labels

# Load draws and plot marginals and contrasts

```{r plot-marginals}
#########

# Update covariate labels
# Add contrasts where appropriate (see hypotheses Rmd documents)

#########

intercept <- 0                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 1 # + Demographics

@@

# Name labels
level_labels <- c(
  str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
  str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
  "Financial transparency: Yes",
  "Accountability: Yes",
  str_c("Funding sources: ", c("Handful of wealthy private donors", "Government grants")),
  str_c("Relationship with host government: ", c("Criticized", "Under crackdown"))
)

# Name covariates
if (public_affairs == 1) {
    "Follow national news: Multiple times a day to Never", "Follow international news: Always to Never", 

@@

      c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters", "News app")

@@

    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: No"

@@

if (political_ideology == 1) {
    "Liberal to Conservative"

@@

if (social_views == 1) {
    "Trust in political institutions: None to Complete", "People should be more charitable: Agree to Disagree",
    "Religious and worship service attendance: Multiple times a week to Never", "Importance of religion: Extremely to Not at all",

@@

      c("Protestant", "Christian Orthodox", "Jewish", "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other")

@@

if (charity_voluntarism == 1) {
    "Importance of trusing charities: Not at all to Essential", "Trust in charities: None to Complete", "Donation frequency: Weekly to Never",
    "Donated last year: $1-$49 to $10,000 or more", "Volunteered in past 12 months: No", "Volunteer frequency: Weekly to Every few years",
    "History of activism: Extreme to Never", "History of family activism: Extreme to Never", 

@@

@@

        "Church or religious organization: ", "Sport or recreational organization: ", "Art, music, or educational organization: ",
        "Labor union: ", "Political party: ", "Environmental organization: ", "Professional association: ", 
        "Humanitarian or charitable organization: ", "Consumer organization: ", "Other organization: "

@@

      "Member to Not"

@@

if (demographics == 1) {

@@

@@

    "Education: Less than high school to Doctorate",
    "Income: Less than $10,000 to $300,000 or more",

@@

      c("White", "Black or African American", "American Indian or Alaska Native", "Asian", "Native Hawaiian or Pacific Islander", "Other")

@@

    "Age: Under 18 to 85 or older"

@@

@@

    # Public affairs
    "Follow national news: Multiple times a day to Never", "Follow international news: Always to Never", 
      c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters", "News app")
    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: No",
    # Political ideology
    "Liberal to Conservative"

@@

    # Public affairs
    "Follow national news: Multiple times a day to Never", "Follow international news: Always to Never", 
      c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters", "News app")
    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: No",
    # Political ideology
    "Liberal to Conservative",
    # Social views
    "Trust in political institutions: None to Complete", "People should be more charitable: Agree to Disagree",
    "Religious and worship service attendance: Multiple times a week to Never", "Importance of religion: Extremely to Not at all",
      c("Protestant", "Christian Orthodox", "Jewish", "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other")

@@

    # Public affairs
    "Follow national news: Multiple times a day to Never", "Follow international news: Always to Never", 
      c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters", "News app")
    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: No",
    # Political ideology
    "Liberal to Conservative",
    # Social views
    "Trust in political institutions: None to Complete", "People should be more charitable: Agree to Disagree",
    "Religious and worship service attendance: Multiple times a week to Never", "Importance of religion: Extremely to Not at all",
      c("Protestant", "Christian Orthodox", "Jewish", "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other")
    # Charity and voluntarism
    "Importance of trusing charities: Not at all to Essential", "Trust in charities: None to Complete", "Donation frequency: Weekly to Never",
    "Donated last year: $1-$49 to $10,000 or more", "Volunteered in past 12 months: No", "Volunteer frequency: Weekly to Every few years",
    "History of activism: Extreme to Never", "History of family activism: Extreme to Never", 
        "Church or religious organization: ", "Sport or recreational organization: ", "Art, music, or educational organization: ",
        "Labor union: ", "Political party: ", "Environmental organization: ", "Professional association: ", 
        "Humanitarian or charitable organization: ", "Consumer organization: ", "Other organization: "
      "Member to Not"

@@

    # Public affairs
    "Follow national news: Multiple times a day to Never", "Follow international news: Always to Never", 
      c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters", "News app")
    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: No",
    # Political ideology
    "Liberal to Conservative",
    # Social views
    "Trust in political institutions: None to Complete", "People should be more charitable: Agree to Disagree",
    "Religious and worship service attendance: Multiple times a week to Never", "Importance of religion: Extremely to Not at all",
      c("Protestant", "Christian Orthodox", "Jewish", "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other")
    # Charity and voluntarism
    "Importance of trusing charities: Not at all to Essential", "Trust in charities: None to Complete", "Donation frequency: Weekly to Never",
    "Donated last year: $1-$49 to $10,000 or more", "Volunteered in past 12 months: No", "Volunteer frequency: Weekly to Every few years",
    "History of activism: Extreme to Never", "History of family activism: Extreme to Never", 
        "Church or religious organization: ", "Sport or recreational organization: ", "Art, music, or educational organization: ",
        "Labor union: ", "Political party: ", "Environmental organization: ", "Professional association: ", 
        "Humanitarian or charitable organization: ", "Consumer organization: ", "Other organization: "
      "Member to Not"
    # Demographics
    "Education: Less than high school to Doctorate",
    "Income: Less than $10,000 to $300,000 or more",
      c("White", "Black or African American", "American Indian or Alaska Native", "Asian", "Native Hawaiian or Pacific Islander", "Other")
    "Age: Under 18 to 85 or older"

@@

# # Create matrix of Gammas.
# gamma_draws <- draws %>% 
#   group_by(i, j) %>% 
#   summarize(gamma_mean = mean(Gamma))
# 
# gamma_matrix <- matrix(as.matrix(gamma_draws)[,3], nrow = max(draws$j), ncol = max(draws$i))
# write.csv(gamma_matrix, file = here::here("analysis", "output", "posterior_means.csv"))

# Plot marginals
# if (intercept == 1) {
#   draws %>% 
#     mutate(
#       levels = factor(i, labels = level_labels)
#     ) %>%
#     ggplot(aes(x = Gamma, y = levels)) + 
#     geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
#     # geom_halfeyeh(.width = .95) +
#     geom_vline(xintercept = 0, color = "grey") +
#     labs(y = "Attribute Levels")
# }

# if (intercept != 1) {
#   draws %>% 
#     filter(j != 1) %>% 
#     mutate(
#       levels = factor(i, labels = level_labels), 
#       covariates = factor(j, labels = covariate_labels)  
#     ) %>%
#     ggplot(aes(x = Gamma, y = covariates)) +
#        geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
#        # geom_halfeyeh(.width = .95) +
#        geom_vline(xintercept = 0, color = "white") +
#        labs(y = "Covariates") +
#        facet_wrap(~ levels, ncol = 5)
# }

# # Save plot
# if (intercept == 1) file_name <- paste("intercept_marginal-posteriors.png")
# if (public_affairs == 1) file_name <- paste("public-affairs_marginal-posteriors.png")
# if (political_ideology == 1) file_name <- paste("political-ideology_marginal-posteriors.png")
# if (social_views == 1) file_name <- paste("social-views_marginal-posteriors.png")
# if (charity_voluntarism == 1) file_name <- paste("charity-voluntarism_marginal-posteriors.png")
# if (demographics == 1) file_name <- paste("demographics_marginal-posteriors.png")
# if (public_political == 1) file_name <- paste("public-political_marginal-posteriors.png")
# if (public_political_social == 1) file_name <- paste("public-political-social_marginal-posteriors.png")
# if (public_political_social_charity == 1) file_name <- paste("public-political-social-charity_marginal-posteriors.png")
# if (public_political_social_charity_demo == 1) file_name <- paste("public-political-social-charity-demos_marginal-posteriors.png")
# ggsave(
#   file_name,
#   path = here::here("analysis", "output", "figures"),
#   width = ifelse(intercept == 1, 12, 20), 
#   height = ifelse(sum(intercept, public_affairs, political_ideology, social_views, charity_voluntarism, demographics) == 1, 12, 20), 
#   units = "in"
# )
```

As an experiment, it might be helpful to use a heatmap to identify where there are significant differences in the non-intercept models, which can then be narrowed down using the marginal plots.

```{r heatmaps}
if (public_affairs == 1) plot_title <- paste("Public Affairs")
if (political_ideology == 1) plot_title <- paste("Political Ideology")
if (social_views == 1) plot_title <- paste("Social Views")
if (charity_voluntarism == 1) plot_title <- paste("Covariates related to charity and voluntarism")
if (demographics == 1) plot_title <- paste("Demographics")
if (public_political == 1) plot_title <- paste("Public Affairs and Political Ideology")
if (public_political_social == 1) plot_title <- paste("Public Affairs, Political Ideology, and Social Views")
if (public_political_social_charity == 1) plot_title <- paste("Public Affairs, Political Ideology, Social Views, and Charity and Voluntarism")
if (public_political_social_charity_demo == 1) plot_title <- paste("Public Affairs, Political Ideology, Social Views, Charity and Voluntarism, and Demographics")

>>>>

# Load draws and plot marginals, contrasts, and heatmaps

Now that we have the draws extracted, we can load draws from the model of interest and plot marginals, contrasts, and heatmaps.

## Load draws and assign labels

```{r load-draws}
intercept <- 1                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

@@

# Assign level labels
level_labels <- c(
  str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
  str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
  "Financial transparency: Yes",
  "Accountability: Yes",
  str_c("Funding sources: ", c("Handful of wealthy private donors", "Government grants")),
  str_c("Relationship with host government: ", c("Criticized", "Under crackdown"))
)

# Assign covariate covariates
public_affairs_labels <- c(
  # *Q2.1*: How often do you follow national news? 
    "Follow national news: ", 
    c("Once a week", "At least once a day")
  # *Q2.3*: Which mediums do you use to follow news? (Select all that apply.)

@@

      "TV", "Print", "Online (excluding social media)", "Social media", 
      "Radio", "Email newsletters", "News app"

@@

  # *Q2.4*: How often would you say you follow what's going on in government and public affairs?
  "Follow government and public affairs: Often", 
  # *Q5.7*: Have you ever traveled to a developing country? 
  "Traveled to a developing country: No"

@@

political_ideology_labels <- c(
  # *Q5.2*: On a scale of extremely liberal (1) to extremely conservative (7), how would you describe your political views?
    "Liberal to Conservative: ", 
      "Somewhat liberal", "Slightly liberal", "Moderate",
      "Slightly conservative", "Somewhat conservative", "Extremely conservative"

@@

social_views_labels <- c(
  # *Q5.6*: On a scale of no trust (1) to complete trust (7), how much do you trust political institutions and the state?
    "Trust in political institutions: ", 
      "Very little trust", "Little trust", 
      "Neutral", "Some trust", "A lot of trust", "Complete trust"
  # *Q5.11*: On a scale of strongly agree (1) to strongly disagree (7), rate your response to the following statement: People should be more charitable towards others in society.
    "People should be more charitable: ", 
      "Agree", "Somewhat agree", "Neutral", 
      "Somewhat disagree", "Disagree", "Strongly disagree"
  # *Q5.8*: How often do you attend religious or worship services, not including weddings and funerals?
    "Religious and worship service attendance: ", 
    c("Rarely", "At least once a month")
  # *Q5.9*: How important is religion in your life?
  "Importance of religion: Important",
  # *Q5.10*: What is your current religion, if any?

@@

      "Protestant", "Christian Orthodox", "Jewish", "Muslim", 
      "Sikh", "Hindu", "Buddhist", "Atheist", "Other"

@@

charity_voluntarism_labels <- c(
  # *Q2.7*: On a scale of not at all important (1) to essential (7), how important is it for you to trust charities?

@@

    "Importance of trusing charities: ", 

@@

      "Very unimportant", "Somewhat unimportant", 
      "Neutral", "Somewhat important", "Very important", "Essential"

@@

  # *Q2.8*: On a scale of no trust at all (1) to complete trust (7), how much do you trust charities?
    "Trust in charities: ", 
      "Very little trust", "Little trust", 
      "Neutral", "Some trust", "A lot of trust", "Complete trust"
  # *Q2.5*: How often do you donate to charity (with either cash or in-kind)?
  "Donation frequency: At least once a month",
  # *Q2.6*: How much did you donate to charity last year?
    "Donated last year: ",
      "$50-$99", "$100-$499", "$500-$999", 
      "$1000-$4,999", "$5000-$9,999", "$10,000+"
  # *Q2.9*: Have you volunteered in the past 12 months?
  "Volunteered in past 12 months: Yes", 
  # *Q2.10*: How often do you volunteer?
    "Volunteer frequency: ",
    c("Rarely", "More than once a month, less than once a year", "At least once a month")
  # *Q5.4*: Historically, how involved have you been in activist causes?
  "History of activism: Involved",
  # *Q5.5*: Historically, how involved has your family been in activist causes?
  "History of family activism: Involved",
  # *Q5.3*: Here is a list of different types of voluntary organizations. For each organization, indicate whether you are an active member, an inactive member, or not a member of that type of organization:
    "Church or religious organization: ",
    c("Inactive member", "Active member")
    "Sport or recreational organization: ",
    c("Inactive member", "Active member")
    "Art, music, or educational organization: ",
    c("Inactive member", "Active member")
    "Labor union: ",
    c("Inactive member", "Active member")
    "Political party: ",
    c("Inactive member", "Active member")
    "Environmental organization: ",
    c("Inactive member", "Active member")
    "Professional association: ",
    c("Inactive member", "Active member")
    "Humanitarian or charitable organization: ",
    c("Inactive member", "Active member")
    "Consumer organization: ",
    c("Inactive member", "Active member")
    "Other organization: ",
    c("Inactive member", "Active member")

@@

demographics_labels <- c(
  # *Q5.12*: What is your gender?

@@

  # *Q5.13*: Are you now married, widowed, divorced, separated, or never married?

@@

  # *Q5.14*: What is the highest degree or level of school you have completed?
    "Education: ", 
      "High school graduate", 
      "Some college", "2 year degree", "4 year degree", 
      "Graduate or professional degree", "Doctorate"
  # *Q5.15*: What is your annual household income before taxes?
  "Income: More than median",
  # *Q5.16*: Choose one or more races that you consider yourself to be:

@@

      "White", "Black or African American", "American Indian or Alaska Native", 
      "Asian", "Native Hawaiian or Pacific Islander", "Other"

@@

  # *Q5.17*: How old are you?
  "Age: More than median"

@@

if (public_affairs == 1) covariate_labels <- public_affairs_labels
if (political_ideology == 1) covariate_labels <- political_ideology_labels
if (social_views == 1) covariate_labels <- social_views_labels
if (charity_voluntarism == 1) covariate_labels <- charity_voluntarism_labels
if (demographics == 1) covariate_labels <- demographics_labels

@@

  covariate_labels <- c(public_affairs_labels, political_ideology_labels)

@@

  covariate_labels <- c(public_affairs_labels, political_ideology_labels, social_views_labels)

@@

    public_affairs_labels, political_ideology_labels, 
    social_views_labels, charity_voluntarism_labels

@@

    public_affairs_labels, political_ideology_labels, 
    social_views_labels, charity_voluntarism_labels, demographics_labels

@@

```

## Plot marginals

```{r plot-marginals}
# Plot marginals
if (intercept == 1) {
  draws %>%
    mutate(
      levels = factor(j, labels = level_labels)
    ) %>%
    ggplot(aes(x = Gamma, y = levels)) +
    geom_halfeye(.width = .95) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>%
    filter(j != 1) %>%
    mutate(
      levels = factor(i, labels = level_labels),
      covariates = factor(j, labels = covariate_labels)
    ) %>%
    ggplot(aes(x = Gamma, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       # geom_halfeyeh(.width = .95) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}

# Save plot
if (intercept == 1) file_name <- paste("intercept_marginal-posteriors.png")
if (public_affairs == 1) file_name <- paste("public-affairs_marginal-posteriors.png")
if (political_ideology == 1) file_name <- paste("political-ideology_marginal-posteriors.png")
if (social_views == 1) file_name <- paste("social-views_marginal-posteriors.png")
if (charity_voluntarism == 1) file_name <- paste("charity-voluntarism_marginal-posteriors.png")
if (demographics == 1) file_name <- paste("demographics_marginal-posteriors.png")
if (public_political == 1) file_name <- paste("public-political_marginal-posteriors.png")
if (public_political_social == 1) file_name <- paste("public-political-social_marginal-posteriors.png")
if (public_political_social_charity == 1) file_name <- paste("public-political-social-charity_marginal-posteriors.png")
if (public_political_social_charity_demo == 1) file_name <- paste("public-political-social-charity-demos_marginal-posteriors.png")
ggsave(
  file_name,
  path = here::here("analysis", "output", "figures"),
  width = ifelse(intercept == 1, 12, 20),
  height = ifelse(sum(intercept, public_affairs, political_ideology, social_views, charity_voluntarism, demographics) == 1, 12, 20),
  units = "in"
)
```

## Plot contrasts

```{r plot-contrasts}

```

## Plot heatmaps

Instead of plotting marginals or contrasts, we can use a heatmap to identify where there are significant differences in the non-intercept models, which can then be narrowed down using the marginal plots.

```{r plot-heatmaps}
if (public_affairs == 1) plot_title <- paste("Public Affairs")
if (political_ideology == 1) plot_title <- paste("Political Ideology")
if (social_views == 1) plot_title <- paste("Social Views")
if (charity_voluntarism == 1) plot_title <- paste("Covariates related to charity and voluntarism")
if (demographics == 1) plot_title <- paste("Demographics")
if (public_political == 1) plot_title <- paste("Public Affairs and Political Ideology")
if (public_political_social == 1) plot_title <- paste("Public Affairs, Political Ideology, and Social Views")
if (public_political_social_charity == 1) plot_title <- paste("Public Affairs, Political Ideology, Social Views, and Charity and Voluntarism")
if (public_political_social_charity_demo == 1) plot_title <- paste("Public Affairs, Political Ideology, Social Views, Charity and Voluntarism, and Demographics")
